Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-16 src/tex/ms.tex
vertical violin plot

\begin{figure*}
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 71 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The blue horizontal solid line represents the median of the restricted posterior of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval of the restricted posterior of $\kappa$.
        The pink horizontal solid line represents $\kappa=0$.
        GW200129 is shown with light blue edges, as it is excluded from the calculation of collective analysis.
    }
    \label{fig:violin_kappa}
\end{figure*}

>>>>

\begin{figure}
    \script{violin_kappa.py}
    \includegraphics[width=\columnwidth]{figures/violin_kappa.pdf}
    \caption{
        Individual-event $\kappa$ posteriors (distributions), and joint measurement (blue band, 90\% CI; blue line, median).
%        Each violin represents a different event.
%        The color of the violins represents the quotient of the median and standard deviation of the posterior.
%        The blue horizontal solid line represents the median of the restricted posterior of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval of the restricted posterior of $\kappa$.
%        The pink horizontal solid line represents $\kappa=0$.
%        GW200129 is shown with light blue edges, as it is excluded from the calculation of collective analysis.
    }
    \label{fig:violin_kappa}
\end{figure}
